URG analysis of the extended Kondo model with d-wave interaction

### 2024-02-01 dWaveESIAM.tex
--no-message

\usepackage{amsmath}

@@

\section{RG scheme}
At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ \vec q \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\). The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{\vec q\right\}\):
\begin{equation}\begin{aligned}
	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1}W_{\vec q_1, \vec q_1, \vec q_1, \vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)^2~.
\end{aligned}\end{equation}
where \(\tau = \hat n - 1/2\). The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the Ising interaction energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.

The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ \vec q \right\} \):
\begin{equation}\begin{aligned}
	H_X^{(j)} =& \underbrace{\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec k, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec k,\sigma} + \text{h.c.}\right]}_{T_1^\dagger + T_1} \\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_2^\dagger + T_2}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}}_{T_4}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime} + \text{h.c.}\right]}_{T_6 + T_6^\dagger}~.
\end{aligned}\end{equation}
The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\). Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of participating states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\). The renormalisation of the Hamiltonian is constructed from the general expression
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

@@

The first term is of the form
\begin{equation}\begin{aligned}
	T_2^\dagger G T_6 = \sum \sigma_1\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} c^\dagger_{\vec q_1, \sigma_1}c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} \frac{1}{\omega - H_D}\sigma_1\sigma_2^\prime W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} \hat n_{\vec q_2,\sigma_2^\prime}c^\dagger_{\vec k_2^\prime,\sigma_1}c_{\vec q_1,\sigma_1}~.
\end{aligned}\end{equation}
The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\), where \(W_{\vec q_1}\) is a shorthand for \(W_{\vec q_1,\vec q_1,\vec q_1,\vec q_1}\). The number operator \(\hat n_{\vec q_2,\sigma_2^\prime}\) projects the initial state to that in which \(\vec q_2\) is occupied. The operator \(c_{\vec q_1,\sigma_1}\) can be combined with its hermitian conjugate on the other side to give another number operator, leading to another projection. Both the number operators reduce to unity upon acting on the projected states:
\begin{equation}\begin{aligned}
	T_2^\dagger G T_6 = \sum \sigma_1^2\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_2^\prime,\sigma_1}\frac{1}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}\sum_{\sigma_2^\prime}\sigma_2^\prime  ~.
\end{aligned}\end{equation}
Since there is a sum over the spin factor \(\sigma_2^\prime = \pm 1\), this term vanishes identically. The particle-hole transformed term \(T_6^\dagger G T_2\) vanishes for the same reason.

We now consider the second term \(T_3^\dagger G T_3\):
\begin{equation}\begin{aligned}
	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\\
			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
\end{aligned}\end{equation}
where \(\vec q_1, \vec q_2\) are summed over all momentum states in the isoenergetic shell and in the particle sector (PS) (states are occupied in the ground state).

The particle-hole transformed term is \(T_3 G T_3^\dagger\):
\begin{equation}\begin{aligned}
	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
\end{aligned}\end{equation}
where the hole projectors \(\left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right)\) force the momenta \(\vec q_1,\vec q_2\) to extend over all states in the hole sector (states that are unoccupied in the ground state). The change in the sign of \(\left[\varepsilon(q_1) + \varepsilon(q_2)\right]\) in the denominator compared to the denominator in \(T_3^\dagger G T_3\) is for the same reason.

The remaining sets of terms that we need to consider are:
\begin{equation}\begin{aligned}
	T_4 G T_4 &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec q_2,\sigma^\prime} \frac{1}{\omega - H_D}W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma}c_{\vec q_1,\sigma}\\
		  &= \frac{1}{4}\sum \hat n_{\vec q_1,\sigma} \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma} \frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}  \\
		  &= -\frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma}c_{\vec k_2,\sigma} \sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~.
\end{aligned}\end{equation}

>>>>

\usepackage{amsmath,hyperref}

@@

\section{RG scheme}
At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ \vec q \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\). The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{\vec q\right\}\):
\begin{equation}\begin{aligned}
	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1}W_{\vec q_1, \vec q_1, \vec q_1, \vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)^2~.
\end{aligned}\end{equation}
where \(\tau = \hat n - 1/2\). The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the Ising interaction energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.

The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ \vec q \right\} \):
\begin{equation}\begin{aligned}
	H_X^{(j)} =& \underbrace{\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec k, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec k,\sigma} + \text{h.c.}\right]}_{T_1^\dagger + T_1} \\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_2^\dagger + T_2}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}}_{T_4}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} + \text{h.c.}\right]}_{T_6^\dagger + T_6}~,\\
		   & \underbrace{+\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec q^\prime, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec q^\prime,\sigma}\right]}_{T_7}~.\\
\end{aligned}\end{equation}
The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\). Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of participating states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\). The renormalisation of the Hamiltonian is constructed from the general expression
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

@@

\subsection{Correlated scattering involve one electron on the shell \(\varepsilon_j\)}
The first term is of the form
	T_6^\dagger G T_2 = \sum \sigma_1\sigma_1^\prime W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1}c_{\vec q_1,\sigma_1} \frac{1}{\omega - H_D}W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2} \left(-\hat n_{\vec q_2,\bar\sigma_1}c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1} + \hat n_{\vec q_2,\sigma_1}c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1} \right.\\
	\left.+ c^\dagger_{\vec q_1,\sigma_1}\left(1 - \hat n_{\vec q_2,\bar\sigma_1}\right) c_{\vec k_2,\sigma_1}\right)~.
The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\), where \(W_{\vec q_1}\) is a shorthand for \(W_{\vec q_1,\vec q_1,\vec q_1,\vec q_1}\). We consider the first two terms for now. The number operators \(\hat n_{\vec q_2,\sigma_1}, \hat n_{\vec q_2,\bar\sigma_1}\) project the initial state to that in which \(\vec q_2\) is occupied, henceforth referred to as the particle sector (PS). The operator \(c_{\vec q_1,\sigma_1}\) can be combined with its Hermitian conjugate on the other side to give another number operator, leading to another projection. Since the two terms are otherwise identical, their opposite signs lead to them cancelling each other. The remaining term involves the hole projection operator \(1 - \hat n_{\vec q_2,\sigma_1}\) which projects onto the set of initial states in which the momentum state \(\vec q_2\) is unoccupied, henceforth referred to as the hole sector (HS). Evaluating this term in the same way leads to
\begin{equation}\begin{aligned}\label{t2t61}
	T_2^\dagger G T_6 = -\sum_{\left\{\vec k_i\right\}, \sigma_1\sigma_1^\prime}  c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_1,\sigma_1} c_{\vec k_2,\sigma_1}\sum_{\vec q_1\in\text{PS},\atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_1}}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}  ~.
The particle-hole transformed term \(T_6^\dagger G T_2\) can be evaluated in the same way:
\begin{equation}\begin{aligned}\label{t6dagt2}
	T_6^\dagger G T_2 = \sum W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2}\left(-c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{\vec q_2,\bar\sigma_1} + c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{\vec q_2,\sigma_1} + c^\dagger_{\vec q_1,\sigma_1}\left(1 - \hat n_{\vec q_2,\bar\sigma_1}\right) c_{\vec k_2,\sigma_1}\right) \frac{1}{\omega - H_D}\times \\
	\sigma_1\sigma_1^\prime W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1}c_{\vec q_1,\sigma_1} ~.
For such a scattering process, the excited energy is given by \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = \frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\). The change of the sign in front of \(\varepsilon(\vec q_1)\) arises from the fact that in this process, the state \(\vec q_1\) is occupied in the intermediate excited state, owing to the \(c^\dagger_{\vec q_1,\sigma_1}\) operator to the right of the Greens function. Cancelling the first two terms in eq.~\ref{t6dagt2} (just as in the previous process) and evaluating the last term gives
\begin{equation}\begin{aligned}\label{t2t62}
	T_6^\dagger G T_2 = \sum_{\left\{\vec k_i\right\}, \sigma_1\sigma_1^\prime}  c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1} c_{\vec k_2,\sigma_1}\sum_{\vec q_1, \vec q_2\in\text{HS}}\frac{W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2}}{\omega - \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}~.

We now assume that the Brillouin zone of the lattice in which our conduction bath is embedded is symmetrical about the Fermi surface. This essentially amounts to working at particle-hole symmetry, by setting the chemical potential of the bath to zero. This symmetry leads to two consequences:
\begin{itemize}
	\item If this is the case, the states in the particle sector will reside on the isoenergetic shell of energy \(-|\varepsilon_j|\), while those in the hole sector will reside at energy \(|\varepsilon_j|\), at equal distances from the Fermi surface (which lies at zero energy). This ensures that in the denominators of the RG equation, we have the simplification 
\begin{equation}\begin{aligned}
	\varepsilon(\vec q_1)\bigg|_\text{PS} = -\varepsilon(\vec q_2)\bigg|_\text{HS} = -|\varepsilon_j|~.
\end{aligned}\end{equation}
\item We also consider the symmetry of of the coupling \(W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2}\) to reflections about the nodal point in the same quadrant of the Brillouin zone. For any momentum \(\vec q_1\) in the hole sector, we can find a corresponding point \(\vec \tilde q_1\) in the particle sector by reflecting about the nodal point. This corresponds to the transformation \(q_x \to \pi - q_x, q_y \to \pi - q_y\), leading to a sign change of the factor \(\left[\cos\left( aq_1^x \right) - \cos\left( aq_1^y \right) \right]\). This leaves the product \(W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}\) unchanged. The diagonal coupling \(W_{\vec q_1}\) also remains unchanged by themselves, since it involves a product of four copies of the factor.
\end{itemize}
These two features ensure that the inner summations over \(\vec q_1,\vec q_2\) are identical in eqs.~\ref{t2t61} and \ref{t2t62}, leading to the vanishing of the total renormalisation \(T_6^\dagger G T_2 + T_2^\dagger G T_6\).

\subsection{Scattering across the Fermi surface involving two electrons on the shell \(\varepsilon_j\)}
We now consider the second term \(T_3^\dagger G T_3\):
\begin{equation}\begin{aligned}
	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma}\\
			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_1,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
\end{aligned}\end{equation}
where \(\vec q_1, \vec q_2\) are summed over all momentum states in the isoenergetic shell and in the particle sector (PS) (states are occupied in the ground state).

The particle-hole transformed term is \(T_3 G T_3^\dagger\):
\begin{equation}\begin{aligned}
	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k_1,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
\end{aligned}\end{equation}
where the hole projectors \(\left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right)\) force the momenta \(\vec q_1,\vec q_2\) to extend over the states only in the hole sector (states that are unoccupied in the ground state). The change in the sign of \(\left[\varepsilon(q_1) + \varepsilon(q_2)\right]\) in the denominator compared to the denominator in \(T_3^\dagger G T_3\) is for the same reason.
